Reproduction of Civic Honesty around the Globe

### 2021-03-24 outputs/paper/paper.Rmd
Update paper.Rmd

## Description of Dataset
This type of the dataset is a csv file, it is imported from the Harvard Dataverse Repository and uploaded June 15th, 2019 [@citeDataverse]. There were 57 variables and 17,303 observations, but we selected 12 variables using the R programming language [@citeR] and the ‘tidyverse’ package [@citeTidyverse]. The selected variables are: id, country (unique numeric code for each country), Country (the name of the country), city, institution (drop-off locations), cond (no money, money, and big money conditions), response (reported or not), age, above40 (the estimated age of the recipient), male (the gender of the recipient), coworkers, computer, other_bystanders. All of those attributes are coded as numerical values except for Country, which is code as alphabetical values. The key variables are response, country, cond, and response: the response variable was used as a dependent variable, the no money condition was used as a control variable, and the other two conditions were used as treatments.

In the original dataset, there were two variables which may cause confusion due to their similarity: ‘country’ with lower case ‘c’ and ‘Country’ with upper case ‘C’. We used the ‘janitor’ package’s ‘clean_names” function to change the names to ‘country’ and ‘country_2’ to avoid confusion [@citeJanitor].

@@

In addition, the estimation of the assistants can be incorrect, and eventually they might record false information during the data collection process. For example, in terms of the ‘Recipient age’ category, the assistants had to guess the recipient’s age and select one from six options: < 20, 20-30, 30-40, 40-50, 50-60, and > 60. What if the recipient looks 30? The assistants might choose either 20-30 or 30-40 based on their judgement since it is a huge challenge to correctly guess someone's age by looking at his or her face. A research team from the Department of Computer Science and Engineering at Michigan State University studied the ability of humans to estimate age using face images collected from crowdsourcing and found that the accuracy of guessing the age correctly with a margin of error of plus/minus 5 years is between 50% and 70% [@citeAgeEstimation]. Namely, there are high chances that the assistants might have recorded inaccurate information for some of those variables that require the researcher's estimation. As a consequence, this can lead to distorted results of the analysis.

Figure \@ref(fig:figReportedByCountry) is a replica of a dumbbell plot included in the original research paper, which shows share of returned (reported) wallets in NoMoney and Money conditions by country. As can be seen in the figure, people were more likely to return wallets with more money in most of the countries selected for the research. If so, can we say that people tend to return wallets contained more money in "most countries"?

@@

## Power Analysis
We ran power analysis to check whether the research team used an appropriate sample size for the original paper. Firstly, we calculated the proportions of the returned wallets in the control group (the ‘no money’ condition) and the treatment group (‘the ‘money’ condition), using the raw data using the dplyr’s select, group_by, summarise, and mutate functions [@citeDplyr]. Then, we calculated the effect size, using the formula written by Stephane Champely [@citePwrPdf]. Lastly, we ran the two-sample test for proportions to estimate the required sample size which is required to show a significant difference between the two groups, using the ‘pwr’ package [@citePwr]. The result of the test shows that the most appropriate size of a sample to compare the two condition groups is 313 for each. Since the sample size of the control group is 7,888 and that of the treatment group is 8,211, we can say that the sample size is large enough to find a statistically significant difference between the two groups. The result of the power analysis is displayed below.

```{r, echo = FALSE, message = FALSE}
#### Line chart: Reporting rates as a function of monetary stakes ####

@@

>>>>

## Description of Dataset
This type of the dataset is a csv file, it is imported from the Harvard Dataverse Repository and uploaded June 15th, 2019 [@citeDataverse]. There were 57 variables and 17,303 observations, but we selected 12 variables using the `R` programming language [@citeR] and the `tidyverse` package [@citeTidyverse]. The selected variables are: id, country (unique numeric code for each country), Country (the name of the country), city, institution (drop-off locations), cond (no money, money, and big money conditions), response (reported or not), age, above40 (the estimated age of the recipient), male (the gender of the recipient), coworkers, computer, other_bystanders. All of those attributes are coded as numerical values except for Country, which is code as alphabetical values. The key variables are response, country, cond, and response: the response variable was used as a dependent variable, the no money condition was used as a control variable, and the other two conditions were used as treatments.

In the original dataset, there were two variables which may cause confusion due to their similarity: ‘country’ with lower case ‘c’ and ‘Country’ with upper case ‘C’. We used the `janitor` package’s ‘clean_names” function to change the names to ‘country’ and ‘country_2’ to avoid confusion [@citeJanitor].

@@

In addition, the estimation of the assistants can be incorrect, and eventually they might record false information during the data collection process. For example, in terms of the ‘Recipient age’ category, the assistants had to guess the recipient’s age and select one from six options: < 20, 20-30, 30-40, 40-50, 50-60, and > 60. What if the recipient looks 30? The assistants might choose either 20-30 or 30-40 based on their judgment since it is a huge challenge to correctly guess someone's age by looking at his or her face. A research team from the Department of Computer Science and Engineering at Michigan State University studied the ability of humans to estimate age using face images collected from crowdsourcing and found that the accuracy of guessing the age correctly with a margin of error of plus/minus 5 years is between 50% and 70% [@citeAgeEstimation]. Namely, there are high chances that the assistants might have recorded inaccurate information for some of those variables that require the researcher's estimation. As a consequence, this can lead to distorted results of the analysis.

Figure \@ref(fig:figReportedByCountry) is a replica of the dumbbell plot included in the original research paper, which shows share of returned (reported) wallets in NoMoney and Money conditions by country. And, Figure \@ref(fig:figMonetaryStakes) is a replica of the line plot included in the paper, which showsshare of returned (reported) wallets in the three conditions; NoMoeny, Money, and BigMoney. We filtered the raw dataset using the `dplyr` package [@citeDplyr] and display the data in a dumbbell plot and line plot using the `ggplot` [@citeGgplot2]. As can be seen in the figures, people were more likely to return wallets with more money in most of the countries selected for the research, and the reporting rate increases if wallets contain bigger money. If so, can we say that people tend to return wallets contained bigger money in "most countries"?

@@

```{r figMonetaryStakes, echo = FALSE, message = FALSE, fig.cap="Reporting rates as a function of monetary stakes"}
#### Line chart: Reporting rates as a function of monetary stakes ####

@@

## Power Analysis
We ran power analysis to check whether the research team used an appropriate sample size for the original paper. Firstly, we calculated the proportions of the returned wallets in the control group (the ‘no money’ condition) and the treatment group (‘the ‘money’ condition), using the raw data using the `dplyr`’s select, group_by, summarise, and mutate functions [@citeDplyr]. Then, we calculated the effect size, using the formula written by Stephane Champely [@citePwrPdf]. Lastly, we ran the two-sample test for proportions to estimate the required sample size which is required to show a significant difference between the two groups, using the `pwr` package [@citePwr]. The result of the test shows that the most appropriate size of a sample to compare the two condition groups is 313 for each. Since the sample size of the control group is 7,888 and that of the treatment group is 8,211, we can say that the sample size is large enough to find a statistically significant difference between the two groups. The result of the power analysis is displayed below.
